The Ultraviolet Radiation Environment of a Tropical Megacity in Transition: Mexico City 2000-2019

### 2021-07-12 Paper_third_version/Article_UV_Mexico.tex
Add references limit and change ylabel of RD OMI vs measurements
Add last change before thrid revision

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  Tropical regions experience naturally high levels of UV radiation, but
  urban pollution can reduce these levels substantially. We analyzed 20
  years of measurements of the UV Index (UVI) at several ground-level
  locations in the Mexico City Metropolitan Area and compared these data
  with UVI values derived from satellite observations of ozone
  and clouds (but not local pollution). The ground-based measurements were
  systematically lower than the satellite-based estimates, by ca. 40\% in
  2000 and 20\% in 2019. Calculations with a radiative transfer model and
  observed concentrations of air pollutants explained well the difference
  between satellite- and ground-based UVI, and showed specific
  contributions from aerosols in the boundary layer and the free troposphere,
  O\textsubscript{3}, NO\textsubscript{2}, and SO\textsubscript{2}, in
  decreasing order of importance. Such large changes in UV radiation
  between 2000 and 2019 have important implications ranging from human
  health (skin cancer and cataract induction) to air pollution control
  (photochemical smog formation).
\end{abstract}

@@

The UVI is recognized by the World Health and Meteorological
Organizations (WHO and WMO) as a standardized measure of UV
radiation\cite{who2002} for global public information. An advantage
of using the UVI as (one) measure of UV radiation is that it is being
increasingly observed or calculated and disseminated, enabling more
objective comparisons among seasons and locations. The UVI observations
from Mexico City, considered here, are an important element of this
global picture.

@@

The Mexico City Metropolitan Area is located at 19.4°N, 99.1°W, 2240
meters above sea level (m asl), surrounded by mountain ridges exceeding
5000 m asl, with complex topography and thermal inversions that inhibit
winds and favor intense air pollution.\citep{Whiteman_2000,Fast_2007,Carre_n_Sierra_2015}
Air quality
monitoring and surface meteorological measurements in the MCMA are
conducted continuously by the Automated Atmospheric Monitoring Network
(RAMA, by its Spanish acronym) of the Atmospheric Monitoring System
(SIMAT, by its Spanish acronym) of the Mexico City government. Since the
year 2000, UV radiometers (model 501-A, Solar Light Company Inc.,
Glenside, PA) detecting wavelengths between 280-400 nm have been
measuring erythemally-weighted solar radiation. The calibration of the
UV sensors has been carried out annually by comparing against a
factory-calibrated reference sensor. The output voltages from the
network’s sensors have been compared for at least one week against the UV
readings from the reference sensor to derive a calibration factor. New
calibration factors typically differ from the old ones by 2\% or less.
Reference sensors have been also calibrated by the manufacturer and updated
periodically (between 3 to 5 years) to reduce systematic errors due to drifts in sensitivity.
Long term calibration drift are minimized by these yearly re-calibrations.
Although at the beginning only a few stations were in operation and have
been changing, currently 11 stations are recording erythemal
irradiances, which are then multiplied by 40 (see
Eq.~{\ref{eq:UVI}}) to give UV Indices.
Table~{\ref{table:stations}} describes the location of
the stations where the UV Index has been measured.
Figure~{\ref{fig:map}} shows how the radiometers of the
SIMAT have been distributed over MCMA, prioritizing sites with higher population density.
Near real-time data for each station are
available on the SIMAT official
website~\url{http://www.aire.cdmx.gob.mx/default.php}. Daily maximum
values (\(UVI_{\max}\)) were extracted~in each of the stations
around solar noon from the time interval from 11:00 h-15:00 h CST
(Central Standard Time). This database~with 7305 continuous days of
measurements during the period 2000-2019 was analyzed.

@@

With the aim to explore the relationship between UVI and air pollutants
levels, the hourly averages for ozone (O\textsubscript{3}), carbon
monoxide (CO), nitrogen dioxide (NO\textsubscript{2}), sulfur
dioxide~(SO\textsubscript{2}) and particle matter with diameter
sizes~\(\le\) 10 ~$\mu$m (PM\textsubscript{10}), were downloaded
from the SIMAT.\cite{pollutants_data} For purposes of assessing the
influence on the UV Index at solar noon, only values obtained between
11h and 15h CST were considered for the trends analysis. Pollutant
measurements are conducted by the SIMAT using regulatory-grade
commercial instruments. Measurement principles include ultraviolet
photometry (model 400E, Teledyne-API) for O\textsubscript{3},
chemiluminescence (model 200E, Teledyne-API) for NO\textsubscript{2}, UV
fluorescence (model 100E, Teledyne API) for SO\textsubscript{2}, and
infrared absorption (model 300E, Teledyne-API) for CO. The
PM\textsubscript{10} continuous mass concentration was measured with
Tapered Element Oscillating Microbalance (TEOM 1400AB or TEOM 1405 DF,
Thermo Scientific) monitors. Gaseous pollutant levels are reported in
ppb concentration units for O\textsubscript{3}, SO\textsubscript{2} and
NO\textsubscript{2}, and in ppm for CO. Particulate matter mass
concentration is reported in $\mu$g m\textsuperscript{-3} at local
conditions for temperature and pressure.

@@

The UV Index data derived from satellite-based measurements
were used for comparison with the ground-based measurements.
These data were provided by the Ozone Monitoring
Instrument (OMI)~on board of AURA-NASA satellite.\citep{dcio} OMI
is operated in cooperation between the Netherlands Agency for Aerospace
Programmes (NIVR), the Finnish Meteorological Institute (FMI) and NASA.
OMI performs observations over a geographical area of 13$\times$24km\textsuperscript{2} at nadir. For
the coordinates (19.33°N, 99.18°W) and elevation (2268 m asl) of Mexico City,
the satellite overpass time is between 19:00h - 21:00h UTC (20:00h - 22:00h CET).
The OMI instrument measures reflected and backscattered radiances of the atmosphere-surface system at several UV wavelengths. The ozone column is estimated by differential absorption of several adjacent
wavelengths in the O\textsubscript{3} Huggins band\citep{Veefkind_2006}, while clouds are estimated from the reflectivity at a wavelength not affected by O\textsubscript{3} absorption (360 nm, \citet{Tanskanen_2007}). A correction for absorbing aerosols is made using a global aerosol climatology.\citep{Arola_2009}
The UV Index used for Mexico City corresponds to values at local noon time and clear sky
from OMUVB Level 2 OVP data product, version 1.3 and collection 3.

@@

Above the atmospheric boundary layer, the model atmosphere was specified to be,
NO\textsubscript{2}, or SO\textsubscript{2}. In one
sensitivity study, a total AOD of 0.7 was redistributed placing 0.2 in
the free troposphere (decreasing vertically with an exponential scale
height of 4 km, and 0.5 remaining in the BL). The calculated UVI
differed by less than 1\%. Thus, as long as the total AOD is known,
knowledge of the exact vertical aerosol profile is not critical for
ground-level UVI, but would obviously affect the vertical structure of
photolysis frequencies.

@@

Figure~{\ref{628947}} shows the diurnal variation of
the UVI for several specific cloud-free days, for different seasons and
several locations (CHO, MER, MON, PED, SAG, SFE and TLA). UV Index calculated with
the TUV model was used as reference of the behavior during clear sky days.
According to the comparison of measurements minute by minute, the dates
with prolonged fluctuations along the day were discarded. However,
during the rainy period (from June to October) at least a brief episode of clouds,
as shown at CHO station around noon in 13 June
2017. Peak values range from 8 during autumn/winter to above 12
in spring/summer, in correspondence to the respective December and June
solstices. Although the stations are all within a 25 km radius,
substantial differences among them are notable. Survey of the locations
revealed that shadowing from nearby structures is not an issue. The good
agreement in the morning, followed by more divergence in the afternoon,
is consistent with the development of photo-chemical pollution hotspots
during the day. Previous studies (e.g., \citet{Castro_2001} and
\citet{Palancar_2013}) have shown
that surface UV radiation in Mexico City is attenuated significantly by
aerosols. The measurements shown in Fig.~{\ref{628947}}
are consistent with this increasing pollution during the course of the
day, with highest aerosol loading (and highest variability) attained in
the afternoon. Further support for the role of pollution in suppressing
the UVI comes from the observation made at the Santa Fe (SFE) site which
in Fig.~{\ref{628947}} are seen to be systematically
higher, e.g. by over 10\% in autumn afternoons, compared to the other
stations. The SFE station is displaced to the west from the majority of
the other stations, and remains in the outskirts. This site is also
approximately 300 m higher than Mexico City downtown, so that the cleaner atmosphere at SFE
is a result of the station’s location farther away from pollution sources,
both horizontally and vertically.\citep{SEDEMA2018a} It is indeed expected to have
higher values of the UVI, in agreement with the observations.

@@

The daily maximum UV Index of each station is denoted
by~\(UVI_{\max}\), these values were counted in the period 2000-2019.
As shown in Figure~{\ref{461017}}, these values ranged
from 1 to 16, with a majority (61\%) of the days
experienced~\(UVI_{\max}\) values between 6 and 10, and remarkably
few, less than 1\%, in the 13-16 range.~The lowest values are
likely due to winter days with heavy cloud cover and low sun angles, and
UV attenuation by pollutants could also be amplified under such
conditions, due to longer photon path lengths at low sun and within
clouds. The extreme sparsity of high UVI values remains surprising, and
may be an indication of the rarity of extremely unpolluted days within
the city.

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.49\columnwidth]{figures/Histogram}
    \caption{{Frequency distribution of daily maximums UV Index values in Mexico City
    during 2000 -2019.
    {\label{461017}}%
    }}
  \end{center}
\end{figure}

Similar patterns are found when considering the monthly average of
the~\(UVI_{\max}\)~values as shown in
Figure~{\ref{310112}}. The long-term averages present a
seasonal variation (as in Fig.~{\ref{628947}}) that
follows approximately the cosine of the noontime solar zenith angle.
Notably, values rarely if ever exceed 12 (as in
Fig.~{\ref{461017}}). The lowest average UVI (near 7)
occurs in winter while from March to August the values seem to be
flattened in the range 10-11. The rather low monthly UV Index values
could be a consequence of the presence of clouds in the rainy
season. However, urban aerosol pollution sources, biomass burning for
agriculture and wood cooking also contribute to poor air quality between
March-May~\citep{Retama_2015}. Using the
maximum~\(UVI_{\max}\) from all of stations every day (one daily
point), the monthly averages (\(\overline{UVI}_m\))
were calculated along the period 2000-2019 (except for June 2003 due to there were no measurements).
Long term trends in~\(\overline{UVI}_m\) are shown
in Figure~{\ref{185758}}. A clear~upward trend is seen,
with a slope for the linear fit of 0.9\%/year or +1.5 UVI units over the
two decades.

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.70\columnwidth]{figures/Boxplotcos}
    \caption{{Boxplot of the monthly averages of the maximum UV Index values~(black
          dot) in MCMA for the period 2000-2019: median (central bold line),
          interquartile range (box edges), 10\% and 90\% percentiles (the whiskers),
          the minimum and maximum values (asterisk) and the cosine of the solar zenith angle at solar
          noon (blue curve).
            {\label{310112}}%
        }}
  \end{center}
\end{figure}

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.70\columnwidth]{figures/UV_Moving_Average}
    \caption{{3-month running average (violet segments curve) applied to monthly
          average UV Index (black line), the standard deviation (blue fill area) and linear fit (red line).
            {\label{185758}}%
        }}
  \end{center}
\end{figure}

The UV Index computed from satellite-based observations
over the period 2005-2019 is shown in
Figure~{\ref{485116}}. The satellite-derived UVIs vary
from 8 in winter to 16 in summer, these values being substantially higher
than the ground-based observations (ca. 7 for winter and 11 for summer,
see Fig.~{\ref{310112}}). The maximum values are reached in June and July of each year for both data sets.
We hypothesize that this large difference between satellite-based estimation and ground-based
observation of the UV index is due to the intense air pollution of
Mexico City.~A rather similar behavior was detected in Santiago city,
Chile.\citep{Cabrera_2012} Although the OMI data are corrected for climatological aerosol absorption\citep{Arola_2009}, this correction likely underestimates the absorption within the polluted Mexico City BL.

@@

\subsection{Effect of pollutants on UV radiation}

@@

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.63\columnwidth]{figures/pollutants}
    \caption{{Air quality trends in MCMA for the period 2000-2019~ from annual
    averages obtained between 11h to 15h CST every day: PM\textsubscript{10}
    (brown curve), CO (purple curve), NO\textsubscript{2} (blue curve),
    SO\textsubscript{2}(black curve), O\textsubscript{3} (green curve) and
    AOD\textsubscript{340} (pink curve).
    {\label{829996}}%
    }}
  \end{center}
\end{figure}

\begin{table}[H]
  \centering
  \begin{tabular}{cccc} \hline
    Variable               & $\frac{absolute change}{year}$ & Avg$_{2000-2019}$ & $\Delta(\%/year)$ \\ \hline
    UVI                    & 0.08                           & 9.2               & 0.9               \\
    PM\textsubscript{10}   & -0.10                          & 50.2              & -0.2              \\
    CO                     & -0.08                          & 1.0               & -8.2              \\
    NO\textsubscript{2}    & -0.96                          & 28.6              & -3.4              \\
    O\textsubscript{3}     & -1.05                          & 61.3              & -1.7              \\
    AOD\textsubscript{340} & -0.01                          & 0.6               & -1.6              \\
    SO\textsubscript{2}    & -0.76                          & 8.4               & -9.1              \\
    \hline
  \end{tabular}
  \caption{{{{UV Index and criteria pollutants: the absolute change per year for the period 2000-2019,
                averages in units of $\mu g/m^3$(PM$_{10}$), ppm (CO), ppb
                (SO$_2$, NO$_2$ and O$_3$), dimensionless (UV Index and AOD$_{340}$) and
                annual percentage change (\%/year).}}}}
  \label{table:uvindex}
\end{table}

The observed changes in the concentrations of these air pollutants have
significant implications for surface UV radiation, as can be
demonstrated with the TUV radiative transfer model.
Table~{\ref{table:TUVmodel}} summarizes UVI values for
the June-July time period, estimated by the three methods: OMI
satellite-derived UVI, SIMAT ground-based observations, and TUV modeling
using air pollution estimates. Two groups of values can be readily
identified: (1) SIMAT daily record values, OMI with or without BL
aerosols, and TUV for very clean conditions, all with UVI values around
15-16; and (2) the average of daily maxima of SIMAT observations and TUV UVI results using
MCMA pollutants as input. Note that SIMAT and TUV values are in good agreement
for both 2018-2019 and 2000-2001 and are considerably lower than for case (1). Compared to the OMI
estimate that included the climatological aerosol correction (15.3),
observed SIMAT values were lower by 35\% in 2000 and by 20\% in 2019.
Similarly, TUV values were 35\% lower in 2000 and 22\% lower in 2019
relative to the TUV values of 15.6 for a pristine atmosphere.

\begin{table}[H]
  \centering
  \begin{tabular}{lc}
    \hline
    \textbf{Conditions for estimation in June-July} & \textbf{UV Index} \\ \hline
    SIMAT average maxima 2000-2001                  & 9.9  $\pm$  1.2   \\ \hline
    SIMAT average maxima 2018-2019                  & 12.3 $\pm$  1.3   \\ \hline
    SIMAT maximum value reached in period 2000-2019 & 15.0              \\ \hline
    OMI maximum value reached in period 2005-2019   & 16.6              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV "zero" pollution \\ AOD 0, O\textsubscript{3} 0 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                      & 16.1              \\ \hline
    \begin{tabular}[c]{@{}l@{}
      }TUV pristine pollution \\ AOD 0.05, O\textsubscript{3} 10 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                      & 15.6              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV 2019:\\ AOD 0.5, O\textsubscript{3} 50 ppb, NO\textsubscript{2} 20 ppb, SO\textsubscript{2} 1 ppb\end{tabular}                      & 12.1              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV 2000:\\ AOD 0.7, O\textsubscript{3} 70 ppb, NO\textsubscript{2} 40 ppb, SO\textsubscript{2} 20 ppb\end{tabular}                      & 10.2              \\ \hline
  \end{tabular}
  \caption{{UVI maxima for June-July: averages and standard deviation from ground-based data
        for the years 2018-2019 and 2000-2001. UVI maximum value reached in the period 2000-2019 for
        UVI ground-based and the same for satellite in the period 2005-2019. TUV calculations for specified conditions.
      }}
  \label{table:TUVmodel}
\end{table}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  Tropical regions experience naturally high levels of UV radiation, but
  urban pollution can reduce these levels substantially. We analyzed 20
  years of measurements of the UV Index (UVI) at several ground-level
  locations in the Mexico City Metropolitan Area and compared these data
  with UVI values derived from satellite observations of ozone
  and clouds (but not local pollution). The ground-based measurements were
  systematically lower than the satellite-based estimates, by ca. 35\% in
  2000 and 20\% in 2019. Calculations with a radiative transfer model and
  observed concentrations of air pollutants explained well the difference
  between satellite- and ground-based UVI, and showed specific
  contributions from aerosols in the boundary layer and the free troposphere,
  O\textsubscript{3}, NO\textsubscript{2}, and SO\textsubscript{2}, in
  decreasing order of importance. Such large changes in UV radiation
  between 2000 and 2019 have important implications ranging from human
  health (skin cancer and cataract induction) to air pollution control
  (photochemical smog formation).
\end{abstract}

@@

The UVI is recognized by the World Health and Meteorological
Organizations (WHO and WMO) as a standardized index of UV
radiation\cite{who2002} for global public information. An advantage
of using the UVI as (one) measure of UV radiation is that it is being
increasingly observed or calculated and disseminated, enabling more
objective comparisons among seasons and locations. The UVI observations
from Mexico City, considered here, are an important element of this
global picture.

@@

The Mexico City Metropolitan Area is located at 19.4°N, 99.1°W, 2240
meters above sea level (m asl), surrounded by mountain ridges exceeding
5000 m asl, with complex topography and thermal inversions that inhibit
winds and favor intense air pollution.\citep{Whiteman_2000,Fast_2007,Carre_n_Sierra_2015}
Air quality
monitoring and surface meteorological measurements in the MCMA are
conducted continuously by the Automated Atmospheric Monitoring Network
(RAMA, by its Spanish acronym) of the Atmospheric Monitoring System
(SIMAT, by its Spanish acronym) of the Mexico City government. Since the
year 2000, UV radiometers (model 501-A, Solar Light Company Inc.,
Glenside, PA) detecting wavelengths between 280-400 nm have been
measuring erythemally-weighted solar radiation. Calibration of the
UV sensors has been carried out annually by comparing against a
factory-calibrated reference sensor. The output voltages from the
network’s sensors have been compared for at least one week against the UV
readings from the reference sensor to derive new calibration factors, which typically differed
from the old ones by 2\% or less.
Reference sensors have been also calibrated by the manufacturer and updated
periodically (between 3 to 5 years) to reduce systematic errors due to drifts in sensitivity.
Long term calibration drifts are minimized by these yearly re-calibrations.
Although at the beginning only a few stations were in operation and
varied, currently 11 stations are recording erythemal
irradiances, which are then multiplied by 40 (see
Eq.~{\ref{eq:UVI}}) to give UV Indices.
Table~{\ref{table:stations}} describes the location of
the stations where the UV Index has been measured.
Figure~{\ref{fig:map}} shows how the radiometers of the
SIMAT have been distributed over MCMA, prioritizing sites with higher population density.
Near real-time data for each station are
available on the SIMAT official
website~\url{http://www.aire.cdmx.gob.mx/default.php}. Daily maximum
values (\(UVI_{\max}\)) were extracted~in each of the stations
around solar noon from the time interval from 11:00 h-15:00 h CST
(Central Standard Time). This database~with 7305 continuous days of
measurements during the period 2000-2019 was analyzed.

@@

To explore the relationship between UVI and air pollutants
levels, the hourly averages for ozone (O\textsubscript{3}), carbon
monoxide (CO), nitrogen dioxide (NO\textsubscript{2}), sulfur
dioxide~(SO\textsubscript{2}) and particle matter with diameter
sizes~\(\le\) 10 ~$\mu$m (PM\textsubscript{10}), were downloaded
from the SIMAT.\cite{pollutants_data} For purposes of assessing the
influence on the UV Index at solar noon, only values obtained between
11h and 15h CST were considered for the trends analysis. Pollutant
measurements are conducted by the SIMAT using regulatory-grade
commercial instruments. Measurement principles include ultraviolet
photometry (model 400E, Teledyne-API) for O\textsubscript{3},
chemiluminescence (model 200E, Teledyne-API) for NO\textsubscript{2}, UV
fluorescence (model 100E, Teledyne API) for SO\textsubscript{2}, and
infrared absorption (model 300E, Teledyne-API) for CO. The
PM\textsubscript{10} continuous mass concentration was measured with
Tapered Element Oscillating Microbalance (TEOM 1400AB or TEOM 1405 DF,
Thermo Scientific) monitors. Gaseous pollutant levels are reported in
ppb concentration units for O\textsubscript{3}, SO\textsubscript{2} and
NO\textsubscript{2}, and in ppm for CO. Particulate matter mass
concentration is reported in $\mu$g m\textsuperscript{-3} at local
temperature and pressure.

@@

The UV Index data derived from satellite-based measurements
were used for comparison with the ground-based measurements.
These data were provided by the Ozone Monitoring
Instrument (OMI)~on board of AURA-NASA satellite.\citep{dcio} OMI
is operated collaboratively by the Netherlands Agency for Aerospace
Programmes (NIVR), the Finnish Meteorological Institute (FMI) and NASA.
OMI performs observations over a geographical area of 13$\times$24km\textsuperscript{2} at nadir. For
the coordinates (19.33°N, 99.18°W) and elevation (2268 m asl) of Mexico City,
the satellite overpass time is between 19:00h - 21:00h UTC (20:00h - 22:00h CET).
The OMI instrument measures reflected and backscattered radiances of the atmosphere-surface system at several UV wavelengths. The ozone column is estimated by differential absorption of several adjacent
wavelengths in the O\textsubscript{3} Huggins band\citep{Veefkind_2006}, and is used in a radiative transfer model to estimate clear-sky UVI at the surface. Clouds are estimated from the observed reflectivity at a wavelength not affected by O\textsubscript{3} absorption (360 nm) and the clear-sky UVI is adjusted for their presence. A correction for absorbing aerosols is made using a global aerosol climatology.\citep{Arola_2009}
The UV Index used for Mexico City corresponds to values at local noon time and clear sky
from OMUVB Level 2 OVP data product, version 1.3 and collection 3.

@@

Above the atmospheric boundary layer, the model atmosphere was specified to be free of aerosols,
NO\textsubscript{2}, or SO\textsubscript{2}. In one
sensitivity study, a total AOD of 0.7 was redistributed placing 0.2 in
the free troposphere (decreasing vertically with an exponential scale
height of 4 km, and 0.5 remaining in the BL). The calculated UVI
differed by less than 1\%. Thus, as long as the total AOD is known,
knowledge of the exact vertical aerosol profile is not critical for
ground-level UVI, though it would obviously affect the vertical structure of
photolysis frequencies.

@@

Figure~{\ref{628947}} shows the diurnal variation of
the UVI for typical cloud-free days, for different seasons and
several locations (CHO, MER, MON, PED, SAG, SFE and TLA).
The selection of cloud-free days was aided by comparison of the measurements
with the TUV model predictions for clear skies, with prolonged deviations and
fluctuations usually indicative of cloudy conditions.However,
during the rainy period (from June to October) at least a brief episode of clouds,
is seen at CHO station around noon in 13 June
2017. Peak values range from 8 during autumn/winter to above 12
in spring/summer, in correspondence to the respective December and June
solstices. Although the stations are all within a 25 km radius,
substantial differences among them are notable. Survey of the locations
revealed that shadowing from nearby structures is not an issue. The good
agreement in the morning, followed by more divergence in the afternoon,
is consistent with the development of photo-chemical pollution hotspots
during the day. Previous studies (e.g., \citet{Castro_2001} and
\citet{Palancar_2013}) have shown
that surface UV radiation in Mexico City is attenuated significantly by
aerosols. The measurements shown in Fig.~{\ref{628947}}
are consistent with this increasing pollution during the course of the
day, with highest aerosol loading (and highest variability) attained in
the afternoon. Further support for the role of pollution in suppressing
the UVI comes from the observation made at the Santa Fe (SFE) site which
in Fig.~{\ref{628947}} are seen to be systematically
higher, e.g. by over 10\% in autumn afternoons, compared to the other
stations. The SFE station is displaced to the west from the majority of
the other stations, and remains in the outskirts. This site is also
approximately 300 m higher than Mexico City downtown, so that the cleaner atmosphere at SFE
is a result of the station’s location farther away from pollution sources,
both horizontally and vertically.\citep{SEDEMA2018a} It is indeed expected to have
higher values of the UVI, in agreement with the observations.

@@

The daily maximum UV Index values of each station,~\(UVI_{\max}\),
are summarized in Figure~{\ref{461017}} for the entire period 2000-2019.
These values are seen to range
from 1 to 16, with a majority (61\%) of the days
experiencing~\(UVI_{\max}\) values between 6 and 10, and remarkably
few, less than 1\%, in the 13-16 range.~The lowest values are
likely due to winter days with heavy cloud cover and low sun angles, and
UV attenuation by pollutants could also be amplified under such
conditions, due to longer photon path lengths at low sun and within
clouds. The extreme sparsity of high UVI values remains surprising, and
may be an indication of the rarity of extremely unpolluted days within
the city.

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.49\columnwidth]{figures/Histogram}
    \caption{{Frequency distribution of daily maximums UV Index values in Mexico City
    during 2000-2019.
    {\label{461017}}%
    }}
  \end{center}
\end{figure}

Similar patterns are found when considering the monthly average of
the~\(UVI_{\max}\)~values as shown in
Figure~{\ref{310112}}. The long-term averages present a
seasonal variation (as in Fig.~{\ref{628947}}) that
follows approximately the cosine of the noontime solar zenith angle.
Notably, values rarely if ever exceed 12 (as in
Fig.~{\ref{461017}}). The lowest average UVI (near 7)
occurs in winter while from March to August the values seem to be
flattened in the range 10-11. The rather low monthly UV Index values
could be a consequence of the presence of clouds in the rainy
season. However, urban aerosol pollution sources, biomass burning for
agriculture and wood cooking also contribute to poor air quality between
March-May~\citep{Retama_2015}. Using the
maximum~\(UVI_{\max}\) from all of stations every day (one daily
point), the monthly averages (\(\overline{UVI}_m\))
were calculated along the period 2000-2019 (except for June 2003 due to lack of measurements).
Long term trends in~\(\overline{UVI}_m\) are shown
in Figure~{\ref{185758}}. A clear~upward trend is seen,
with a slope for the linear fit of 0.9\%/year or +1.5 UVI units over the
two decades.

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.70\columnwidth]{figures/Boxplotcos}
    \caption{{Monthly averages of the maximum UV Index values~(black
          dot) in MCMA for the period 2000-2019: median (central bold line),
          interquartile range (box edges), 10\% and 90\% percentiles (whiskers),
          the minimum and maximum values (asterisk) and the cosine of the solar zenith angle at solar
          noon (blue curve).
            {\label{310112}}%
        }}
  \end{center}
\end{figure}

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.70\columnwidth]{figures/UV_Moving_Average}
    \caption{{Monthly
          average UV Index (black line), the standard deviation (blue fill area) and linear fit (red line).
            {\label{185758}}%
        }}
  \end{center}
\end{figure}

The UV Index computed from OMI satellite-based observations
over the period 2005-2019 is shown in
Figure~{\ref{485116}}. The satellite-derived UVIs vary
from 8 in winter to 16 in summer, these values being substantially higher
than the ground-based observations (ca. 7 for winter and 11 for summer,
see Fig.~{\ref{310112}}). The maximum values are reached in June and July of each year for both data sets.
We hypothesize that this large difference between satellite-based estimation and ground-based
observation of the UV index is due to the intense air pollution of
Mexico City.~A rather similar behavior was detected in the city of Santiago,
Chile.\citep{Cabrera_2012} Although the OMI data are corrected for climatological aerosol absorption\citep{Arola_2009}, this correction likely underestimates the absorption within the polluted Mexico City BL.

@@

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.5]{figures/Monthly_mean_RD.png}
  \caption{Deviation (\%) of satellite-derived UVI from the ground-based monthly means UVI for the period 2005-2019.}
  \label{fig:percentage_relative_difference}
\end{figure}

Figure \ref{fig:percentage_relative_difference} deviation of the OMI-derived UVI from the ground-based monthly averages. The mean percentage relative difference
was 35\% in the period 2005-2019. Comparable UV reductions, of 30-40\% due to aerosols, were reported by
\citet{Panicker_2009} over Pune, India from April 2004 to
March 2005, with sensitivity coefficients (i.e. change in UVI per unit
change in AOD) similar to those found here in Table~\ref{table:TUVmodel}.

Comparisons of OMI with ground-based UV measurements have been reviewed
recently by \citet{Zhang_2019} and \citet{Vitt_2020}.
OMI-derived UV generally overestimates
ground-level measurements by 1-10\% in relatively clean conditions (e.g.
rural U.S), by 10-30\% in Southern Europe and by 40\% or more in
Santiago, Chile\citep{Cabrera_2012} and Thailand\citep{Janjai_2013}. The
overestimations appear related in large part to incomplete accounting of
UV absorption by BL aerosol, although other factors such as the
correction to solar noon may also introduce some
bias.\citep{Zhang_2019} Over Europe, ground-based UVI observations for
several decades are systematically lower than those estimated from
satellites even after consideration of climatological aerosol
distributions, showing the importance of local pollution not resolved
from space.\citep{Vitt_2020} However, the difference between
satellite-derived and ground-based UVI was less than 1.0 UVI units in
over 90\% of the cases, in contrast to the difference of 3-5 units found
here for Mexico City (Table~{\ref{461017}}).

\subsection{Effect of pollutants on UV radiation in Mexico City}

@@

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.55\columnwidth]{figures/pollutants}
    \caption{{Air quality trends in MCMA for the period 2000-2019.~ Annual
    averages obtained between 11h to 15h CST every day: PM\textsubscript{10}
    (brown curve), CO (purple curve), NO\textsubscript{2} (blue curve),
    SO\textsubscript{2}(black curve), O\textsubscript{3} (green curve) and
    AOD\textsubscript{340} (magenta curve).
    {\label{829996}}%
    }}
  \end{center}
\end{figure}

\begin{table}[H]
  \centering
  \begin{tabular}{cccc} \hline
    Variable               & $\frac{absolute change}{year}$ & Avg$_{2000-2019}$ & $\Delta(\%/year)$ \\ \hline
    UVI                    & 0.08                           & 9.2               & 0.9               \\
    PM\textsubscript{10}   & -0.10                          & 50.2              & -0.2              \\
    CO                     & -0.08                          & 1.0               & -8.2              \\
    NO\textsubscript{2}    & -0.96                          & 28.6              & -3.4              \\
    O\textsubscript{3}     & -1.05                          & 61.3              & -1.7              \\
    AOD\textsubscript{340} & -0.01                          & 0.6               & -1.6              \\
    SO\textsubscript{2}    & -0.76                          & 8.4               & -9.1              \\
    \hline
  \end{tabular}
  \caption{{{{Trends of UV Index and criteria pollutants over 2000-2019.
                Units: $\mu g/m^3$ for PM$_{10}$, ppm for CO, ppb for SO$_2$, NO$_2$ and O$_3$.}}}}
  \label{table:uvindex}
\end{table}

The observed changes in the concentrations of these air pollutants have
significant implications for surface UV radiation, as can be
demonstrated with the TUV radiative transfer model.
Table~{\ref{table:TUVmodel}} summarizes UVI values for
the June-July time period, estimated by the three methods: OMI
satellite-derived UVI, SIMAT ground-based observations, and TUV modeling
using air pollution estimates. Two groups of values can be readily
identified: (1) SIMAT daily record values, OMI with or without BL
aerosols, and TUV for very clean conditions, all with UVI values around
15-16; and (2) the average of daily maxima of SIMAT observations and TUV UVI results using
MCMA pollutants as input. Note that SIMAT and TUV value are in good agreement
for both 2000-2001 and 2018-2019 and are considerably lower than for group (1). Compared to the OMI
estimate that included the climatological absorbing aerosol correction (15.3),
observed SIMAT values were lower by 35\% in 2000 and by 20\% in 2019.
Similarly, TUV values were 35\% lower in 2000 and 22\% lower in 2019
relative to the TUV values of 15.6 for a pristine atmosphere.

\begin{table}[H]
  \centering
  \begin{tabular}{lc}
    \hline
    \textbf{June-July}                              & \textbf{UV Index} \\ \hline
    SIMAT average maxima 2000-2001                  & 9.9  $\pm$  1.2   \\ \hline
    SIMAT average maxima 2018-2019                  & 12.3 $\pm$  1.3   \\ \hline
    SIMAT maximum value reached in period 2000-2019 & 15.0              \\ \hline
    OMI maximum value reached in period 2005-2019   & 16.6              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV "zero" pollution \\ AOD 0, O\textsubscript{3} 0 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                      & 16.1              \\ \hline
    \begin{tabular}[c]{@{}l@{}
      }TUV pristine atmosphere \\ AOD 0.05, O\textsubscript{3} 10 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                      & 15.6              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV 2019:\\ AOD 0.05, O\textsubscript{3} 50 ppb, NO\textsubscript{2} 20 ppb, SO\textsubscript{2} 1 ppb\end{tabular}                      & 12.1              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV 2000:\\ AOD 0.7, O\textsubscript{3} 70 ppb, NO\textsubscript{2} 40 ppb, SO\textsubscript{2} 20 ppb\end{tabular}                      & 10.2              \\ \hline
  \end{tabular}
  \caption{{Comparison of June-July UVI maxima measured directly (SIMAT), inferred from satellite-based
        observations (OMI), and modeled for different pollution levels (TUV).
      }}
  \label{table:TUVmodel}
\end{table}
